Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Add paragraph explaining neighborhood column

\subsection{Impact on Milky Way observations} \label{ssec:impact_on_mw}
\subsubsection{The Solar neighborhood} \label{sssec:neighborhood{}}
To gain further handle on the midplane behavior as a function of azimuth, we
compute the range of midplane values for a given $\Delta \phi$ segment of the
midplane in Figure~\ref{fig:range_deltaphi}. With the observer's azimuth set
to zero, we consider a region extending from $-\Delta \phi/2$ to
$\Delta\phi/2$. We also compute the chord length for the chord extending from
the observer to $\pm \Delta\phi/2$. We repeat this for each of the $50$ bins
in azimuth. Each bin is plotted as a gray line, with the mean value in solid
blue and the $1\,\sigma$ dispersion as the dashed blue lines.

@@

>>>>

\subsection{Impact on Milky Way observations} \label{ssec:impact_on_mw}
\subsubsection{The Solar neighborhood} \label{sssec:neighborhood}
To gain further handle on the midplane behavior as a function of azimuth, we
compute the range of midplane values for a given $\Delta \phi$ segment of the
midplane in Figure~\ref{fig:range_deltaphi}. With the observer's azimuth set
to zero, we consider a region extending from $-\Delta \phi/2$ to
$\Delta\phi/2$. We also compute the chord length for the chord extending from
the observer to $\pm \Delta\phi/2$. We repeat this for each of the $50$ bins
in azimuth. Each bin is plotted as a gray line, with the mean value in solid
blue and the $1\,\sigma$ dispersion as the dashed blue lines.

@@

We repeat this entire procedure for each of the orbits of the real open
clusters in Table~\ref{tab:real_clusters} using the midplane variations from
m12i. We use m12i as a conservative choice, since it provides the greatest
midplane variation (Figure~\ref{fig:midplane}). We report the neighborhood
values for the mass of each cluster in the neighborhood column of
Table~\ref{tab:real_clusters}. Except for alphaPer, we find that the
neigbhorhood around each cluster is typically $\gtrsim 500\,\pc$. This
analysis assumes that the midplane from m12i can be accurately applied to
Milky Way orbits, which is not necessarily true. However, our analysis is
meant to be more illustrative than quantitative and these neighborhood numbers
should be understood as such.
